Results

### 2022-01-06 03_analysis/02_results_summary.Rmd
adding analysis by region

---
title: "Results"
#author: "Miles D. Williams"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

**Note**: Table 1 shows results with the imputed dataset. Table 2 shows results with the non-imputed dataset.

@@

>>>>

---
title: "Results"
#author: "Miles D. Williams"
date: "`r Sys.Date()`"
output: pdf_document
header-includes:
  - \usepackage{lscape}
  - \usepackage{pdfpages}
---

@@

**Note**: Table 1 shows full panel results with the imputed dataset. Table 2 shows full panel results with the non-imputed dataset. Tables 3-5 show OLS, IV, and Lewbel IV estimates by region, respectively, for the imputed dataset. Tables 6-8 show the same with the non-imputed dataset.

@@

\newpage
\begin{landscape}

```{r, results='asis'}
load(
  paste0(getwd(), "/ols_region_tab1.R")
)
cat(ols.region)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/ivlag_region_tab1.R")
)
cat(ivlag.region)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/ivlew_region_tab1.R")
)
cat(ivlew.region)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/ols_region_tab2.R")
)
cat(ols.region)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/ivlag_region_tab2.R")
)
cat(ivlag.region)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/ivlew_region_tab2.R")
)
cat(ivlew.region)
```

\end{landscape}
